---
title: "Statistical methods for archaeological<br>data analysis I: Basic methods"
author: "Martin Hinz"
date: "FS 2021"
institute: "Institut für Archäologische Wissenschaften, Universität Bern"
output:
  xaringan::moon_reader:
    keep_md: true
    chakra: libs/remark-latest.min.js
    css: ["libs/default.css", "libs/default-fonts.css", "libs/customize.css"]
    lib_dir: libs
    seal: false
    nature:
      beforeInit: "libs/macros.js"
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      fig_caption: yes
---
class: title-slide
```{r, echo = FALSE}
# https://stackoverflow.com/questions/25646333/code-chunk-font-size-in-rmarkdown-with-knitr-and-latex
def.chunk.hook  <- knitr::knit_hooks$get("chunk")
knitr::knit_hooks$set(chunk = function(x, options) {
  x <- def.chunk.hook(x, options)
  ifelse(options$size != "normalsize", paste0("\\", options$size,"\n\n", x, "\n\n \\normalsize"), x)
})
```

```{r, echo = FALSE, results="asis"}
cat('## ', rmarkdown::metadata$title)
```
.small[
```{r, echo = FALSE, results="asis"}
cat(rmarkdown::metadata$author, "| ")
cat(rmarkdown::metadata$institute, "| ")
cat(rmarkdown::metadata$date)
```
]

<details markdown=1><summary>Content of the Course</summary>
.tiny[
| Nr. | Presentation | Chapter | Video | Technical Videos | Date Live Session | Chapter Shennan | Practical Task |
|:-|:-|:-|:-|:-:|:-:|-:|:-:|
| 1. | [Introduction](01_session/session_1_introduction.html) | tbw | [Video](https://tube.switch.ch/videos/0843b374) | [1](http://vitutr.archaeological.science/statistical%20methods%20for%20archaeological%20data%20analysis%20i%202019/2019/02/12/installing_r.html),[2](http://vitutr.archaeological.science/statistical%20methods%20for%20archaeological%20data%20analysis%20i%202019/2019/02/12/installing_r_studio.html) | 24.2.21 | 1+2 |
| 2. | [Introduction into R](02_session/index.html) | [Chapter](https://martinhinz.github.io/smada2021/book/introduction-into-r.html) | [Part 1](https://tube.switch.ch/videos/b8d09352) [Part 2](https://tube.switch.ch/videos/hbwPCzKup8) | [5](http://vitutr.archaeological.science/statistical%20methods%20for%20archaeological%20data%20analysis%20i%202019/2019/02/22/basic_operations_in_r.html),[6](http://vitutr.archaeological.science/statistical%20methods%20for%20archaeological%20data%20analysis%20i%202019/2019/02/22/data_types_and_variables.html),[7](http://vitutr.archaeological.science/statistical%20methods%20for%20archaeological%20data%20analysis%20i%202019/2019/02/23/working_with_vectors.html),[8](http://vitutr.archaeological.science/statistical%20methods%20for%20archaeological%20data%20analysis%20i%202019/2019/02/23/working_with_matrices_and_data_frames.html),[9](http://vitutr.archaeological.science/statistical%20methods%20for%20archaeological%20data%20analysis%20i%202019/2019/02/24/load_and_save_data.html) | 3., 10. & 17.3.21 | NA |
| 3. | [Explorative Statistics/Graph. Display](03_session/index.html) | [Chapter](https://martinhinz.github.io/smada2021/book/explorative-statistics-graphical-display.html) | NA | [10](http://vitutr.archaeological.science/statistical%20methods%20for%20archaeological%20data%20analysis%20i%202019/2019/03/22/making_tables.html), [11](http://vitutr.archaeological.science/statistical%20methods%20for%20archaeological%20data%20analysis%20i%202019/2019/03/22/plotting.html), [12](http://vitutr.archaeological.science/statistical%20methods%20for%20archaeological%20data%20analysis%20i%202019/2019/03/25/pie_charts.html), [13](http://vitutr.archaeological.science/statistical%20methods%20for%20archaeological%20data%20analysis%20i%202019/2019/03/27/bar_charts.html), [14](http://vitutr.archaeological.science/statistical%20methods%20for%20archaeological%20data%20analysis%20i%202019/2019/04/03/boxplots.html), [15](http://vitutr.archaeological.science/statistical%20methods%20for%20archaeological%20data%20analysis%20i%202019/2019/04/06/scatterplots.html), [16](http://vitutr.archaeological.science/statistical%20methods%20for%20archaeological%20data%20analysis%20i%202019/2019/05/10/cumsum_and_triplots.html) | 24.3.21 | 3 |
| 4. | [Descriptive Statistics](04_session/index.html) | [Chapter](book/descriptive-statistics.html) | [Video](https://tube.switch.ch/videos/yDLbBcbEWD) | [17](http://vitutr.archaeological.science/statistical%20methods%20for%20archaeological%20data%20analysis%20i%202019/2019/05/17/central_tendency.html), [18](http://vitutr.archaeological.science/statistical%20methods%20for%20archaeological%20data%20analysis%20i%202019/2019/05/18/measurement_of_dispersion.html), [[19](http://vitutr.archaeological.science/statistical%20methods%20for%20archaeological%20data%20analysis%20i%202019/2019/05/23/skewness_and_kurtosis.html)] | 31.3.21 | 4 | [Homework](04_session/homework_04.html) |
| 5. | [Nonparametric Tests](05_session/index.html) | [Chapter](book/nonparametric-tests.html) | [Part 1](https://tube.switch.ch/videos/X9AIAGeD6O), [Part 2](https://tube.switch.ch/videos/A7XnqwrDbP) | [20](http://vitutr.archaeological.science/statistical%20methods%20for%20archaeological%20data%20analysis%20i%202019/2019/05/23/ks_test.html), [22](http://vitutr.archaeological.science/statistical%20methods%20for%20archaeological%20data%20analysis%20i%202019/2019/05/24/chi_square_test.html), [[21](http://vitutr.archaeological.science/statistical%20methods%20for%20archaeological%20data%20analysis%20i%202019/2019/05/24/mann_whitney_U_test.html)], [[23](http://vitutr.archaeological.science/statistical%20methods%20for%20archaeological%20data%20analysis%20i%202019/2019/07/09/associations.html)], [[24](http://vitutr.archaeological.science/statistical%20methods%20for%20archaeological%20data%20analysis%20i%202019/2019/07/09/fisher_test.html)] | 14.4.21 | 5 | [Homework](05_session/homework_05.html) |
| 6. | [Basic Probability Theory](06_session/index.html) | [Chapter](book/basic-probability-theory.html) | [Part 1](https://tube.switch.ch/videos/zOZVOQMqXg), [Part 2](https://tube.switch.ch/videos/TT1pe1qgUQ) | NA | 21.4.21 | 6 | [Homework](06_session/hausaufgabe_06.pdf) |
| 7. | [Parametric Tests](07_session/index.Rmd) | [Chapter](07_session/07-chapter.html) | [Video](https://tube.switch.ch/videos/w9aPnpQxZX) | [25](https://tube.switch.ch/videos/59fee43c), [26](https://tube.switch.ch/videos/xSllWrdxaq), [27](https://tube.switch.ch/videos/pbBEzZY6rj) | 28.4.21 | 6 | [Homework](07_session/hausaufgabe_07.pdf) |
| 8. | Regression & Correlation | Chapter | Video | Technical Videos | 5.5.21 | 8 |  Homework |
| 9. | Cluster Analysis | Chapter | Video | Technical Videos | 12.5.21 | 11 | Homework |
| 10. | Correspondence Analysis | Chapter | Video | Technical Videos | 19.5.21 | 13 | Homework |
| 12. | Repetition | Chapter | Video | Technical Videos | 26.5.21 | NA |
| 11. | Test | Chapter | Video | Technical Videos | 2.6.21 | NA |
]
</details>

### [The book](book/preface.html)

### [Zoom Link for live sessions](https://unibe-ch.zoom.us/j/98025730826) (Mi, 12-14 CET)

### [Zoom Link for virtual office hours](https://unibe-ch.zoom.us/j/96910041917) (Mi, 10-12 CET)

### Slack Workspace: [smada2021.slack.com](https://smada2021.slack.com)

.small[
You can find the **code of this presentations** at the [github repository](https://github.com/MartinHinz/smada2021). You might also like to check out the **video tutorials** in [english](https://tube.switch.ch/channels/b191ef92) or [german](http://vitutr.archaeological.science/).
]