---
title: "Statistical methods for archaeological<br>data analysis I: Basic methods"
author: "Martin Hinz"
date: "FS 2021"
institute: "Institut für Archäologische Wissenschaften, Universität Bern"
output:
  xaringan::moon_reader:
    keep_md: true
    chakra: libs/remark-latest.min.js
    css: ["libs/default.css", "libs/default-fonts.css", "libs/customize.css"]
    lib_dir: libs
    seal: false
    nature:
      beforeInit: "libs/macros.js"
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      fig_caption: yes
---
class: title-slide
```{r, echo = FALSE}
# https://stackoverflow.com/questions/25646333/code-chunk-font-size-in-rmarkdown-with-knitr-and-latex
def.chunk.hook  <- knitr::knit_hooks$get("chunk")
knitr::knit_hooks$set(chunk = function(x, options) {
  x <- def.chunk.hook(x, options)
  ifelse(options$size != "normalsize", paste0("\\", options$size,"\n\n", x, "\n\n \\normalsize"), x)
})
```

```{r, echo = FALSE, results="asis"}
cat('## ', rmarkdown::metadata$title)
```
.small[
```{r, echo = FALSE, results="asis"}
cat('#### ', rmarkdown::metadata$author)
```

```{r, echo = FALSE, results="asis"}
cat(rmarkdown::metadata$institute)
```

```{r, echo = FALSE, results="asis"}
cat(rmarkdown::metadata$date)
```

### Presentations

- [01. Session: Introduction](01_session/session_1_introduction.html) | 24.02.2021
- [02. Session: Introduction into R](02_session/index.html) | 03.03.2021
- [03. Session: Explorative Statistics/Graph. Display](03_session/index.html) | 10.03.2021
- 04\. Session: Descriptive Statistics | 17.03.2021
- 05\. Session: Nonparametric Tests | 24.03.2021
- 06\. Session: Chi-square test | 31.03.2021
- 07\. Session: Probability Theory and Distributions | 14.04.2021
- 08\. Session: Distributions | 21.04.2021
- 09\. Session: Parametric Tests | 28.04.2021
- 10\. Session: Regression & Correlation | 05.05.2021
- 11\. Session: Cluster Analysis | 12.05.2021
- 12\. Session: Correspondence Analysis | 26.05.2021
- Test | 02.06.2021
]

.footnote[
.small[
<sup>\*</sup> You can find the **code of this presentations** at the [github repository](https://github.com/MartinHinz/smada2021). You might also like to check out the **video tutorials** in [english](https://tube.switch.ch/channels/b191ef92) or [german](http://vitutr.archaeological.science/).
]
]